Instructions for \confname{} Proceedings

### 2018-05-17 EMNLP-demo-paper/emnlp2018.tex
update hover

\title{Visual Integration Tool for the Natural Language Inference and Machine Comprehension Tasks}

@@

\section{Introduction}

exploration task

Comparsion with AllenNLP

>>>>

\title{Instructions for \confname{} Proceedings}

@@

\section{Introduction}
The following instructions are directed to authors of papers submitted
to \confname{} or accepted for publication in its proceedings. All
authors are required to adhere to these specifications. Authors are
required to provide a Portable Document Format (PDF) version of their
papers. \textbf{The proceedings are designed for printing on A4
paper.}
